---
title: "Progetto R"
author: "Team"
date: "2023-01-24"
output:
  html_document:
    df_print: paged
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## R Markdown
Variable Label
year Year
country Country
iso ISO 3-letter code
ifs IFS 3-number country-code
pop Population
rgdpmad Real GDP per capita (PPP, 1990 Int$, Maddison)
rgdbarro Real GDP per capita (index, 2005=100)
rconsbarro Real consumption per capita (index, 2006=100)
gdp GDP (nominal, local currency)
iy Investment-to-GDP ratio
cpi Consumer prices (index, 1990=100)
ca Current account (nominal, local currency)
imports Imports (nominal, local currency)
exports Exports (nominal, local currency)
narrowm Narrow money (nominal, local currency)
money Broad money (nominal, local currency)
stir Short-term interest rate (nominal, percent per year)
ltrate Long-term interest rate (nominal, percent per year)
hpnom House prices (nominal index, 1990=100)
unemp Unemployment rate (percent)
wage Wages (index, 1990= 100)
debtgdp Public debt-to-GDP ratio
revenue Government revenues (nominal, local currency)
expenditure Government expenditure (nominal, local currency)
xrusd USD exchange rate (local currency/USD)
peg Peg dummy
peg_strict Strict peg dummy
crisisJST Systemic financial crises (0-1 dummy); included since R5
crisisJST_old Systemic financial crises (0-1 dummy); as coded in all prior releases (R1 – R4)
JSTtrilemmaIV JST trilemma instrument (raw base rate changes)
tloans Total loans to non-financial private sector (nominal, local currency)
tmort Mortgage loans to non-financial private sector (nominal, local currency)
thh Total loans to households (nominal, local currency)
tbus Total loans to business (nominal, local currency)
bdebt Corporate debt (nominal, local currency)
peg_type Peg type (BASE, PEG, FLOAT)
peg_base Peg base (GBR, USA, DEU, HYBRID, NA)
eq_tr Equity total return, nominal. r[t] = [[p[t] + d[t]] / p[t-1] ] - 1
housing_tr Housing total return, nominal. r[t] = [[p[t] + d[t]] / p[t-1] ] - 1
7
bond_tr Government bond total return, nominal. r[t] = [[p[t] + coupon[t]] / p[t-1] ] - 1
bill_rate Bill rate, nominal. r[t] = coupon[t] / p[t-1]
rent_ipolated 1 if housing rental yields interpolated e.g. wartime
housing_capgain_ipol
ated
1 if housing capital gains and total returns interpolated e.g. wartime
housing_capgain Housing capital gain, nominal. cg[t] = [ p[t] / p[t-1] ] - 1
housing_rent_rtn Housing rental return. dp_rtn[t] = rent[t]/p[t-1]
housing_rent_yd Housing rental yield. dp[t] = rent[t]/p[t]
eq_capgain Equity capital gain, nominal. cg[t] = [ p[t] / p[t-1] ] - 1
eq_dp Equity dividend yield. dp[t] = dividend[t]/p[t]
eq_capgain_interp 1 if equity cap. gain interpolated to cover exchange closure
eq_tr_interp 1 if equity total return interpolated to cover exchange closure
eq_dp_interp 1 if equity dividend interpolated or assumed zero to cover exchange closure
bond_rate Gov. bond rate, rate[t] = coupon[t] / p[t-1], or yield to maturity at t
eq_div_rtn Equity dividend return. dp_rtn[t] = dividend[t]/p[t-1]
capital_tr Tot. rtn. on wealth, nominal. Wtd. avg. of housing, equity, bonds and bills
risky_tr Tot. rtn. on risky assets, nominal. Wtd. avg. of housing and equity
safe_tr Tot. rtn. on safe assets, nominal. Equally wtd. avg. of bonds and bills
lev Banks, capital ratio (in %)
ltd Banks, loans-to-deposits ratio (in %)
noncore Banks, noncore funding ratio (in %)

https://www.macrohistory.net/database/

```{r}
library(readxl)
df <- read_excel("Dati macroeconomi.xlsx")

str(df)

```

