---
title: "Progetto R"
author: "Team"
date: "2023-01-24"
output:
  html_document:
    df_print: paged
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## R Markdown
Real Economy

Nominal GDP (local currency), Real GDP per capita (PPP), Real GDP per capita (index, 2005=100), Real Consumption per capita (index, 2006=100), Investment-to-GDP Ratio, Population, Unemployment Rate, Wages (index, 1990=100)

 
International
Current Account (nominal, local currency), Imports (nominal, local currency), Exports (nominal, local currency), USD Exchange Rate (local currency/USD)


Government
Government Revenue (nominal, local currency), Government Expenditure (nominal, local currency), Public Debt-to-GDP Ratio

Money, Prices & Interest Rates
Narrow Money (nominal, local currency), Broad Money (nominal, local currency), Short-term Interest Rate (nominal, percent per year), Long-term Interest Rates (nominal, percent per year), Consumer Prices (index, 1990=100)

Credit Data
Total Loans to Non-financial Private Sector (nominal, local currency), Mortgage Loans to Non-financial Private Sector (nominal, local currency), Total Loans to Households (nominal, local currency), Total Loans to Business (nominal, local currency)

House Prices
House Prices (index, 1990=100)

Crisis Dates
Systemic Financial Crisis (0-1 dummy)

Rates of Return
Equity Total Return, Capital Gain and Dividend Yield; Housing Total Return, Capital Gain and Rental Yield; Government Bond Total Return, Government Bill Rate; Total Rates of Return on Risky and Safe Assets, and on Overall Wealth. All data are nominal, local currency.

 
Peg Data 
Peg (0-1 dummy), Strict Peg (0-1 dummy), Peg Type (Base, Peg, Float), Peg Base

 
Bank Balance Sheet Ratios
Capital Ratio, Loan-to-Deposit Ratio, Noncore Funding Ratio

https://www.macrohistory.net/database/

```{r}
library(readxl)
df <- read_excel("Dati macroeconomi.xlsx")

str(df)

```

