---
title: "Progetto R"
author: "Team"
date: "2023-01-24"
output:
  html_document:
    df_print: paged
editor_options: 
  markdown: 
    wrap: 72
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## R Markdown

Descrizione variabili

Variable Label

-   **year Year**

-   **country Country**

-   iso ISO 3-letter code ifs

-   IFS 3-number country-code pop Population

-   rgdpmad Real GDP per capita (PPP, 1990 Int\$, Maddison)

-   **rgdbarro Real GDP per capita (index, 2005=100)** - andamento nel
    tempo per paese all'interno dell'Eurozona? (chi cresce di più?)
    Gaetano

-   **rconsbarro Real consumption per capita (index, 2006=100)** -
    (parcheggiamo inflazione)

-    **gdp GDP (nominal, local currency)**  - confronto nel tempo del
    GDP (crescita in totale) Gianluca

-   **iy Investment-to-GDP ratio - correlazione tra iy e** **gdp**

    (1 euro investito 5 anni fa è correlato alla crescita) Gaetano

-   cpi Consumer prices (index, 1990=100)  - media prezzi ponderati del
    paniere (inflazione) - esiste una correllazione tra inflazione e
    popolazione? Gabriele

-   ca Current account (nominal, local currency)  - ?

-   imports Imports (nominal, local currency) - Quali Paesi importano
    di + (negli ultimi 10 anni)? Per paese, incidenza del Import sul
    GDP? Gianluca

-   exports Exports (nominal, local currency) - Quali Paesi esportano
    di + (negli ultimi 10 anni) Gianluca

-   narrowm Narrow money (nominal, local currency)

-   money Broad money (nominal, local currency)

-   stir Short-term interest rate (nominal, percent per year)

-   ltrate Long-term interest rate (nominal, percent per year)

-   hpnom House prices (nominal index, 1990=100)

-   unemp Unemployment rate (percent)

-   wage Wages (index, 1990= 100)

-   debtgdp Public debt-to-GDP ratio revenue Government revenues
    (nominal, local currency)

-   expenditure Government expenditure (nominal, local currency)

-   xrusd USD exchange rate (local currency/USD)

-   peg Peg dummy peg_strict Strict peg dummy crisisJST Systemic
    financial crises (0-1 dummy);

-   included since R5 crisisJST_old Systemic financial crises (0-1
    dummy);

-   as coded in all prior releases (R1 -- R4)

-   JSTtrilemmaIV JST trilemma instrument (raw base rate changes)

-   tloans Total loans to non-financial private sector (nominal, local
    currency)

-    tmort Mortgage loans to non-financial private sector (nominal,
    local currency)

-   thh Total loans to households (nominal, local currency)

-   tbus Total loans to business (nominal, local currency)

-   bdebt Corporate debt (nominal, local currency)

-   peg_type Peg type (BASE, PEG, FLOAT)

-   peg_base Peg base (GBR, USA, DEU, HYBRID, NA)

-   eq_tr Equity total return, nominal. r[t] = [[p[t] + d[t]] / p[t-1]
    ] - 1 housing_tr Housing total return,

-   nominal. r[t] = [[p[t] + d[t]] / p[t-1] ] - 1 7 bond_tr Government
    bond total return,

-   nominal. r[t] = [[p[t] + coupon[t]] / p[t-1] ] - 1 bill_rate Bill
    rate, nominal.

-    r[t] = coupon[t] / p[t-1] rent_ipolated 1 if housing rental yields
    interpolated e.g. wartime housing_capgain_ipol ated 1 if housing
    capital gains and total returns interpolated e.g. wartime
    housing_capgain Housing capital gain, nominal. cg[t] = [ p[t] /
    p[t-1] ] - 1 housing_rent_rtn Housing rental return. dp_rtn[t] =
    rent[t]/p[t-1] housing_rent_yd Housing rental yield. dp[t] =
    rent[t]/p[t] eq_capgain Equity capital gain, nominal. cg[t] = [ p[t]
    / p[t-1] ] - 1 eq_dp Equity dividend yield. dp[t] = dividend[t]/p[t]
    eq_capgain_interp 1 if equity cap. gain interpolated to cover
    exchange closure eq_tr_interp 1 if equity total return interpolated
    to cover exchange closure eq_dp_interp 1 if equity dividend
    interpolated or assumed zero to cover exchange closure bond_rate
    Gov. bond rate, rate[t] = coupon[t] / p[t-1], or yield to maturity
    at t eq_div_rtn Equity dividend return. dp_rtn[t] =
    dividend[t]/p[t-1] capital_tr Tot. rtn. on wealth, nominal. Wtd.
    avg. of housing, equity, bonds and bills risky_tr Tot. rtn. on risky
    assets, nominal. Wtd. avg. of housing and equity safe_tr Tot. rtn.
    on safe assets, nominal. Equally wtd. avg. of bonds and bills lev
    Banks, capital ratio (in %) ltd Banks, loans-to-deposits ratio (in
    %) noncore Banks, noncore funding ratio (in %)

<https://www.macrohistory.net/database/>

```{r}
library(readxl)
df <- read_excel("Dati macroeconomi.xlsx")

str(df)

```
